Response to the defense feedback

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

\subsection{Interpret Instructions Symbolically}
Current binary analysis frameworks~\cite{shoshitaishvili2016state,
  10.1007/978-3-642-22110-1_37, song2008bitblaze} translate machine instructions into
intermediate languages (IR) to simplify analysis since
the variety of machine instructions is
enormous, and their semantics is complex. The Intel Developer
Manual~\cite{intelsys} documents more than 1000 different x86 instructions.
Unfortunately, the IR layer, which
reduces the workload of these tools, is not suitable for side-channels
analysis because
IR-based or source code side-channels analyses do not represent the executed instructions accurately enough to analyze fully their control and memory accesses.
For example, a compiler may use conditional moves or bitwise operations to eliminate
branches. Also, as some IRs are not a superset or a subset of ISA,
it is hard to rule out conditional jumps introduced by IR and add real branches
eliminated by IR transformations.

>>>>

\subsection{Interpret Instructions Symbolically}
Current binary analysis frameworks~\cite{shoshitaishvili2016state,
  10.1007/978-3-642-22110-1_37, song2008bitblaze} translate machine instructions into
intermediate languages (IR) to simplify analysis since
the variety of machine instructions is
enormous, and their semantics is complex. The Intel Developer
Manual~\cite{intelsys} documents more than 1000 different x86 instructions.
Unfortunately, the IR layer, which
reduces the workload of these tools, is not suitable for side-channels
analysis because
IR-based or source code side-channels analyses do not represent the executed instructions accurately enough to analyze fully their control and memory accesses.
For example, a compiler may use conditional moves or bitwise operations to eliminate
branches. Also, as IRs are not a superset or a subset of ISA,
it is hard to rule out conditional jumps introduced by IR and add real branches
eliminated by IR transformations.
